The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-16 paper/main.tex
paper: update text

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This work aims to clarify the biases that stellar binarity introduces
to occurrence rates inferred from transit surveys.
In general, stellar multiplicity leads to diluted planetary 
radii, overestimated detection efficiencies, and an undercounted number of 
selected stars (but possibly an overcounted number of searched stars).
These effects skew occurrence rate measurements in different directions, and 
we develop simple models that allow us to understand the crucial effects.
For a model in which all stellar systems are either single or twin binaries, 
and all planets are identical, we find that ignoring binarity leads to an 
underestimate of the occurrence at the true radius by a multiplicative factor 
of $0.76$ (assuming a 10\% twin binary fraction).
Using more realistic models for the stellar population and planetary 
radii, we find that ignoring binarity leads to a $10$\,-\,$30\%$ 
underestimate of the number of planets per star, depending on the true radius 
distribution.
For the occurrence of Earth-sized planets, in our most realistic model the 
rate is underestimated by $\approx 15\%$~--~at present far smaller than 
systematic uncertainties on real $\eta_\oplus$ measurements.
For hot Jupiters, we find that the inferred occurrence rate is 
$\approx 1.3\times$ smaller than the true rate around single stars.
We suggest that this latter effect contributes to the discrepant hot Jupiter 
rates measured by {\it Kepler}\ and the California group's respective surveys.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of selected stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity fraction 
of {\it selected} stars is greater than that of a volume limited 
sample.
This is the familiar Malmquist bias: binaries are selected out to larger 
distances than single stars because they are more luminous.
As a separate challenge, finding the correct number of detected planets in a 
radius bin, $N_{\rm det}$, requires knowledge of the true planetary radii.
Observers deduce apparent radii.
In binaries, the apparent and true radii differ because of diluting flux, 
and possibly because the planet is assumed to orbit the wrong star
\citep[\textit{e.g.},][]{furlan_kepler_2017}.

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed planets and primaries, varying secondaries;
    \item Model \#3: fixed primaries, varying planets and secondaries.
\end{itemize}
In Sec.~\ref{sec:definitions}, we clarify our terminology and state
assumptions that apply throughout this study.
We then present our transit survey models in 
Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
each subsection corresponds to a model listed above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} connect them to topical questions in 
the interpretation of transit survey occurrence rates.
In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
towards measurements of $\eta_\oplus$, and the implications for detailed 
study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
We conclude in Sec.~\ref{sec:conclusion}.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the searchable volumes for single stars ({\it left}), and 
        twin binaries ({\it right}).
        This model (\#1) assumes all stars have equal mass and luminosity, and 
        all planets have the same true radius $r=r_p$.
        {\it Top:} At an apparent radius $r\a=r_p$,
        the observer selects twin binaries out to a larger         
        distance, $\sqrt{2}\times$ that of single stars.
        Because of dilution, there are no planets in twin binaries with 
        $r\a=r_p$.
        {\it Middle:} At an apparent radius $r\a=r_p/\sqrt{2}$, the 
        searched volumes are half those at $r\a=r_p$. 
        The only detected planets with $r\a=r_p/\sqrt{2}$ orbit twin binaries.
        {\it Bottom:} Planets with a true radius $r=r_p$ are searchable to 
        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
        twin binaries. These distances are the same as what an observer 
        selects based on apparent radii.
    }
    \label{fig:model_1_volumes}
\end{figure}

@@

Since the effects of binarity are most pronounced when the two components are 
similar, we first consider a universe in which all planets are 
identical, and all stars are identical except that some fraction of them exist 
in binaries.
Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized} 
and~\ref{eq:rate_density_shape} the rate density for a selected sample of 
stars at planet radius $r$ is
\begin{equation}
\Gamma_{\rm sel}(r) = \delta(r-r_p) \times
\frac{
    Z_0 +
    \mu (Z_1 + Z_2)
}{1+2\mu},
\label{eq:model_1_rate_density}
\end{equation}
where $\mu$ is given by Eq.~\ref{eq:mu_general} with $f(q) = \delta(q-1)$,
$\delta$ is the Dirac delta function, and the true planet radius is 
$r_p$.
We will generally write rate densities in terms of $\mu$'s, rather than 
$N_i$'s, because $\mu$'s are independent of planet radius.

We return to our group of binarity-ignoring astronomers. They select all the 
points on-sky that they think are searchable: those that are above some flux 
limit (at each $\delta_{\rm obs}$).
The relevant stellar samples are illustrated in Fig.~\ref{fig:model_1_volumes}.
At an apparent radius equal to the true radius ($r\a=r_p$), the observer 
thinks all stars are singles, with $d<d_0$.
In fact, binaries with $r\a=r_p$ are also searchable, out to $\sqrt{2}d_0$. 
However, in this model no such systems exist; all planets in twin binaries 
have true radii $r=r_p$, and so are observed with apparent radii 
$r\a=r_p/\sqrt{2}$.
This is because of ``radius dilution'':
for an unresolved point-source... %TODO FIXME

At an apparent radius of $r\a=r_p/\sqrt{2}$, there might also be planets with 
true radii $r=r_p/\sqrt{2}$ orbiting a single~---~however none of these exist 
in this model either.
Following Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
computed without considering binarity is
\begin{equation}
\Gamma_a(r_a) = 
\frac{1}{1+\mu} Z_0 \cdot
\delta(r\a-r_p)  +
\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
\delta\left(r\a-\frac{r_p}{\sqrt{2}} \right),
\label{eq:model_1_apparent_rate_density}
\end{equation}

@@

To confirm the intuition that non-twin binaries do not affect 
the above result, we now assume $f(q) = q^\beta/\mathcal{N}_q$, for 
$\mathcal{N}_q$ the normalization.
This changes $\mu$ (Eq.~\ref{eq:mu_general}).
It may also affect the rate density, which could be a function of the stellar 
mass, which now changes for secondaries (we assume that singles and primaries 
have the same mass). Absorbing this dependence into a power law as well,
\begin{equation}
\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
\frac{M^\gamma}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry 
the units (each side has units $[r^{-1} M^{-1}]$).
We assume that stars are a one-parameter family, given by $R \propto M \propto 
L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
about a secondary.

@@

For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
1.41425$. %171211_model_integrals.nb
For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.014$; the
apparent rate density is higher than the rate density around singles by 1.4\%.
Although with slightly tedious algebra, the result that for power-law 
radius distribution (at $r\gtrsim 2r_\oplus$), binarity influences derived 
occurrence rates at the $\sim$few percent level seems robust for Sun-like 
stars.

@@

\paragraph{The rate of Earth analogs}
The most immediately arresting result there is a ``bump'' in the apparent rate 
density at $r\a < 2r_\oplus$.
For the case in which secondaries host as many (half as many) planets as 
single stars, this means an overestimate of the absolute occurrence rate by 
$\approx 50\%$ ($\approx 25\%$).
It remains even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.

\paragraph{Hot Jupiter occurrence rates}
Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density
for $r>8r_\oplus$, we can compare the apparent hot Jupiter 
occurrence rate with the true rate for singles.
In the most extreme case of $Z_2/Z_0=0$, we find that $\Lambda_{{\rm 
HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
\begin{equation}
\Lambda_{\rm HJ,a} = \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
\end{equation}
and similarly for $\Lambda_{\rm HJ,0}$.
%occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
If $Z_2/Z_0>0$, binarity affects this value less: when $Z_2/Z_0=0.5$, 
we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Further models: radius gaps, Gaussian HJ distributions}

@@

In particular,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
the radius-period 
plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
The existence of the gap has been independently corroborated from a sample of 
KOIs with asteroseismically-determined stellar 
parameters~\citep{van_eylen_asteroseismic_2017}.
Precise measurement of the gap's features, in particular its width, 
depth, and shape, will require more accurate occurrence rates.
To illustrate binarity's role in the issue, we make identical assumptions as 
in Model \#3, but instead assume an intrinsic radius distribution
\begin{align}
f(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus, \\
0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
{\rm constant} & \text{for } r\leq1.5r_\oplus.
\end{cases}
\right.
\label{eq:model4_radius_distribution}
\end{align}
The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
If left uncorrected, binarity makes the gap appear more shallow, and flattens 
the step-function edges.
Of course, other effects could also ``blur'' the gap in the planet radius 
dimension. 
In particular, the valley's period-dependence is almost certainly not flat
\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
This means that any study assessing its width, depth, etc. only in the planet 
radius dimension must either account for the blurring that comes from 
marginalizing over the periods, or else perform tests at fixed periods.

@@

In the recent work by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
island in period-radius space, rather than as a continuous component of a 
power law distribution.
Consider instead the intrinsic radius shape function
\begin{equation}
f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
\end{equation}
with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.
As always, $\Gamma_i(r) = Z_i f(r)$.
We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
Integrating to find hot Jupiter rates,
we find the opposite effect as from the power law model.
For $Z_2/Z_0>0$, 
the apparent HJ rate is {\it greater} than the true rate for singles.
The effect is maximal when there are as many hot Jupiters orbiting secondaries 
as singles, in which case
$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.84$
For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
\approx \Lambda_{\rm HJ,a}$ to within one percent.

@@

\paragraph{How has binarity been considered in occurrence rate measurements?}
This work has shown that binarity introduces substantial systematic 
uncertainty to star and planet counts.
To first order, it appears not to effect estimates of pipeline completeness...
%TODO
In spite of this fact, stellar multiplicity has mostly been ignored in 
calculations of planet occurrence rates using transit survey data\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
}~
\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
carefully assessed binarity's importance, or lack thereof.
While we do not resolve the problem, we do suggest
the approximate scale of the necessary corrections in a survey-independent 
manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

The high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; Petigura et al.\! 2018,
in preparation).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true completeness, and thus the true 
occurrence rates, will remain biased.
The first-order correction that we suggest, given the impracticality of 
performing high-resolution imaging of every selected star in a transit survey,
is to model the detection pipeline's efficiency while accounting for 
binarity.
%Simply put~--~do not assume binarity can be ignored, and take the relevant 
%systematic uncertainties about the selected stars into account.
For {\it Kepler}, this would require high resolution imaging of a
comparison sample of non-KOI host stars. If the associated multiplicity 
statistics are then included in a model of the pipeline's detection 
efficiency, and the number of selected stars is appropriately counted, it 
would correct most of binarity's biases.

\paragraph{The hot Jupiter rate discrepancy}

There is at least one context in which ignoring binarity may already be 
leading to discrepant measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Based on their measurements, \citeauthor{guo_metallicity_2017}\! 
then argued that the metallicity difference could account for a $\approx 20\%$ 
relative difference in the measured rates between the CKS and {\it Kepler}\ 
samples~--~not a factor of two.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

>>>>

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
Particular attention is paid to dilution of observed planet radii, errors in 
star counts, and detection efficiencies.
Free parameters in our models include the true radius distribution of planets, 
and the relative numbers of planets orbiting secondaries, primaries, and 
single stars.
In the simplest possible case, all stellar systems are either single or twin 
binaries, and all planets are identical. If so, then we find that ignoring 
binarity leads to an underestimate of the occurrence at the true radius by a 
multiplicative factor of $0.76$ (assuming a 10\% twin binary fraction).
Using more realistic models for the stellar population and planetary 
radii, we find that the occurrence of Earth-sized planets can be overestimated 
by at most $\approx 50\%$ when ignoring binarity~--~at present far smaller 
than systematic uncertainties on real $\eta_\oplus$ measurements.
We quantify how gaps in the intrinsic planet radius distribution are filled 
in when binarity is neglected.
Our models suggest that for most of the observed radius distribution 
($r>2r_\oplus$), ignoring binarity only leads to errors in inferred occurrence 
rates at the $\lesssim 10\%$ level.
One corollary is that binarity is unlikely to strongly influence the HJ rate 
discrepancy.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of selected stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity fraction 
of {\it selected} stars is greater than that of a volume limited 
sample.
This is the familiar Malmquist bias: binaries are selected out to larger 
distances than single stars because they are more luminous.
As a separate challenge, finding the correct number of detected planets in a 
radius bin requires knowledge of the true planetary radii.
Observers deduce apparent radii.
In binaries, the apparent and true radii differ because of diluting flux, 
and possibly because the planet is assumed to orbit the wrong star
\citep[\textit{e.g.},][]{furlan_kepler_2017}.

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed primaries, power-law planets, varying secondaries;
    \item Model \#3: fixed primaries, broken power-law planets and varying 
    secondaries.
\end{itemize}
In Sec.~\ref{sec:definitions}, we clarify our terminology and state
assumptions that apply throughout this study.
We then present our transit survey models in 
Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
each subsection corresponds to a model listed above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} connect them to topical questions in 
the interpretation of transit survey occurrence rates.
In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
towards measurements of $\eta_\oplus$, and the implications for detailed 
study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
We conclude in Sec.~\ref{sec:conclusion}.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the searchable volumes for single stars ({\it left}), and 
        twin binaries ({\it right}).
        This model (\#1) assumes all stars have equal mass and luminosity, and 
        all planets have the same true radius $r=r_p$.
        {\it Top:} At an apparent radius $r\a=r_p$,
        the observer searched twin binaries out to a larger         
        distance, $\sqrt{2}\times$ that of single stars.
        Because of dilution, there are no planets in twin binaries with 
        $r\a=r_p$.
        {\it Middle:} At an apparent radius $r\a=r_p/\sqrt{2}$, the 
        searched volumes are half those at $r\a=r_p$. 
        The only detected planets with $r\a=r_p/\sqrt{2}$ orbit twin binaries.
        {\it Bottom:} Planets with a true radius $r=r_p$ are searchable to 
        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
        twin binaries. These distances are the same as what an observer 
        selects based on apparent radii.
    }
    \label{fig:model_1_volumes}
\end{figure}

@@

Since the effects of binarity are most pronounced when the two components are 
similar, we first consider a universe in which all planets are 
identical, and all stars are identical except that some fraction of them exist 
in binaries.
Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized} 
and~\ref{eq:rate_density_shape} the rate density for a selected sample of 
stars at planet radius $r$ is
\begin{equation}
\Gamma_{\rm sel}(r) = \delta(r-r_p) \cdot
\frac{
    Z_0 +
    \mu (Z_1 + Z_2)
}{1+2\mu},
\label{eq:model_1_rate_density}
\end{equation}
where $\mu$ is given by Eq.~\ref{eq:mu_general} with $f(q) = \delta(q-1)$,
$\delta$ is the Dirac delta function, and the true planet radius is 
$r_p$.
We will generally write rate densities in terms of $\mu$'s, rather than 
$N_i$'s, because $\mu$'s are independent of planet radius.

We return to our group of binarity-ignoring astronomers. They select all the 
points on-sky that they think are searchable: those that are above some flux 
limit (at each $\delta_{\rm obs}$).
The relevant stellar samples are illustrated in Fig.~\ref{fig:model_1_volumes}.
At an apparent radius equal to the true radius ($r\a=r_p$), the observer 
thinks all searchable stars are singles, with $d<d_0$.
In fact, binaries with $r\a=r_p$ are also searchable, out to $\sqrt{2}d_0$. 
However, in this model no such systems exist; all planets in twin binaries 
have true radii $r=r_p$, and so are observed with apparent radii 
$r\a=r_p/\sqrt{2}$.
This is because they are ``diluted'':
for an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left({r\a \over R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
sys}(M_a, q)}.
\label{eq:delta_obs_general} 
\end{equation}
At an apparent radius of $r\a=r_p/\sqrt{2}$, there might also be planets with 
true radii $r=r_p/\sqrt{2}$ orbiting a single~---~however none of these exist 
in this model either.
Following Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
computed without considering binarity is
\begin{equation}
\Gamma_a(r_a) = 
\frac{1}{1+\mu} Z_0 \cdot
\delta(r\a-r_p)  +
\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
\delta\left(r\a-\frac{r_p}{\sqrt{2}} \right),
\label{eq:model_1_apparent_rate_density}
\end{equation}

@@

To confirm the intuition that non-twin binaries do not affect 
the above result, we now assume $f(q) = q^\beta/\mathcal{N}_q$, for 
$\mathcal{N}_q$ the normalization.
This changes $\mu$ (Eq.~\ref{eq:mu_general}).
It may also affect the rate density, which could be a function of the stellar 
mass, which is now varying for secondaries (we assume that singles and 
primaries have the same mass).
Absorbing this dependence into a power law as well,
\begin{equation}
\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
\frac{M^\gamma}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry 
the units (each side has units $[r^{-1} M^{-1}]$).
We assume that stars are a one-parameter family, given by $R \propto M \propto 
L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
about a secondary.

@@

For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Eq.~\ref{eq:powerlaw_vary_binary} give $(\ldots)\approx 
1.41425$. %171211_model_integrals.nb
For ${\rm BF}=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.014$; the
apparent rate density is higher than the rate density around singles by 1.4\%.
To summarize, this model suggests that for a power-law radius distribution 
(applicable for $r\gtrsim 2r_\oplus$), binarity influences apparent planet
occurrence rates around Sun-like stars at the $\sim$few percent level.

@@

\paragraph{The rate of Earth analogs}
The most immediately arresting result there is a ``bump'' in the apparent rate 
density at $r\a < 2r_\oplus$: the true rate for singles is less than the 
inferred rate.
For the case in which secondaries host as many (half as many) planets as 
single stars, this means an overestimate of the absolute occurrence rate by 
$\approx 50\%$ ($\approx 25\%$).
The ``bump'' exists even for the $Z_2/Z_0=0$ case as a $\approx 10\%$ effect.

\paragraph{Hot Jupiter occurrence rates}
Taking Fig.~\ref{fig:occ_rate_model_3_log} and integrating the rate density, 
we can compare the apparent hot Jupiter 
occurrence rate with the true rate for singles.
In the most extreme case of $Z_2/Z_0=0$, we find that $\Lambda_{{\rm 
HJ},0}/\Lambda_{\rm HJ,a} = 1.13$, where
\begin{equation}
\Lambda_{\rm HJ,a} = \int_{8r_\oplus}^{\infty} \Gamma\a(r)\,{\rm d}r,
\end{equation}
and similarly for $\Lambda_{\rm HJ,0}$.
%occ_rate_vs_radius_model_3_withtext_Zsub2_0.00_rpu_22.5.pdf
If $Z_2/Z_0>0$, binarity affects this value less: when $Z_2/Z_0=0.5$, 
we find $\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 1.06$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Further models: radius gaps, Gaussian HJ distributions}
\label{sec:further_models}

@@

In particular,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
the radius-period 
plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
The existence of the gap has been independently corroborated from a sample of 
KOIs with asteroseismically-determined stellar 
parameters~\citep{van_eylen_asteroseismic_2017}.
Precise measurement of the gap's features, in particular its width, 
depth, and shape, will require accurate occurrence rates.
To illustrate binarity's role in this problem, we make identical assumptions 
as in Sec.~\ref{sec:model_3}, but instead assume an intrinsic radius 
distribution
\begin{align}
f(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus, \\
0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
{\rm constant} & \text{for } r\leq1.5r_\oplus.
\end{cases}
\right.
\label{eq:model4_radius_distribution}
\end{align}
The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
If left uncorrected, binarity makes the gap appear more shallow, and flattens 
the step-function edges.
Of course, other effects could also ``blur'' the gap in the planet radius 
dimension. 
In particular, the valley's period-dependence is almost certainly not flat
\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
This means that any study measuring the gap's width or depth in the face of 
binarity must either perform tests at fixed orbital period, or else 
marginalize over period and account for the associated blurring in the planet 
radius dimension.

@@

In the recent work by~\citet{petigura_CKS_2017}, hot Jupiters appear as an 
island in period-radius space, rather than as a continuous component of a 
power law distribution.
Consider instead a Gaussian radius shape function,
\begin{equation}
f(r) \propto \exp \left( -\frac{(r-\bar{r})^2}{2\sigma^2} \right),
\end{equation}
with $\bar{r} = 14r_\oplus$ and $\sigma = 2r_\oplus$.
As always, $\Gamma_i(r) = Z_i f(r)$.
We then compute $\Gamma\a(r\a)$, and plot it in Fig.~\ref{fig:gaussian_HJ}.
Integrating to find hot Jupiter rates,
we find the opposite effect as in the power law model.
For $Z_2/Z_0>0$, 
the apparent HJ rate is {\it greater} than the true rate for singles.
The effect is maximal when there are as many hot Jupiters orbiting secondaries 
as singles, in which case
$\Lambda_{{\rm HJ},0}/\Lambda_{\rm HJ,a} = 0.84$
For the case when no hot Jupiters orbit secondaries, $\Lambda_{{\rm HJ},0} 
\approx \Lambda_{\rm HJ,a}$ to within one percent.

@@

\paragraph{How has binarity been considered in occurrence rate measurements?}
This study has shown that under a reasonable set of simplifying assumptions, 
binarity can introduce systematic errors to star and planet counts in transit 
surveys, which then bias derived occurrence rates.
Thus far, real-world occurrence rate calculations\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
} using transit survey data have mostly ignored stellar 
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, 
it seems that no one has yet carefully assessed binarity's importance, or lack 
thereof.
While we do not resolve the problem, we do suggest the approximate scale of 
the necessary corrections in a survey-independent manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

The high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; 
\citealt{petigura_CKS_2017}).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true number of searchable stars, and thus the true 
occurrence rates, will remain biased.
The first-order correction that we suggest, given the impracticality of 
performing high-resolution imaging of every selected star in a transit survey,
is to model the detection pipeline's efficiency while accounting for 
binarity.
For {\it Kepler}, this would require high resolution imaging of a
comparison sample of non-KOI host stars. If the associated multiplicity 
statistics are then included in a model of the pipeline's detection 
efficiency, and the number of selected stars is appropriately counted, it 
would correct many of binarity's biases.

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In our Model \#3, the inferred rate can be up to 50\% higher than the true 
rate around single stars.
Though this bias seems large, it is currently small compared to the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If a future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity has been suggested as 
a possible source of discrepant occurrence rate measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Based on their measurements, \citeauthor{guo_metallicity_2017}\! 
then argued that the metallicity difference could account for a $\approx 20\%$ 
relative difference in the measured rates between the CKS and {\it Kepler}\ 
samples~--~not a factor of two.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.
